Working title: Ecological network control

### 2018-06-14 paper/manuscript.Rmd
Aesthetical improvements to control capacity/ superior plot

```{r fig-species-level, fig.width=fig_sizes()[[2]], fig.height=fig_sizes()[[1]], fig.cap="Control capacity and "}
drake::loadd(fig_control_capacity)
fig_control_capacity %>%
    cowplot::plot_grid(plotlist = .)
```

>>>>

```{r fig-species-level, fig.width=fig_sizes()[[2]]*2/3, fig.height=fig_sizes()[[1]], fig.cap="Control capacity and "}
drake::loadd(fig_control_capacity)
library(ggplot2)
fig_control_capacity[[2]] <- fig_control_capacity[[2]] +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_blank())
fig_control_capacity[[4]] <- fig_control_capacity[[4]] +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_blank())

# pdf("test.pdf", width =fig_sizes()[[2]]*2/3, height = fig_sizes()[[1]])
fig_control_capacity %>%
    cowplot::plot_grid(plotlist = ., rel_widths = c(1.21,1), align = "h")
# dev.off()

```
